---
title: "Demo Code"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document illustrates how to use R code to implement our method proposed in the paper. The code below can be used to conduct the simulation study reported in the main text. Below we simulate and analyze a single data set. For the final simulation we used multiple cores to analyze 100 synthetic datasets for each scenario. The four cases of the simulation study can be specified by changing type and utility in the "Data simulation" section below.


Those R packages need to be installed before running the demo code.
```{r,message=FALSE}
library(fields)
library(MCMCpack)
```

Set working directory where you save all the code files:
```{r}
path <- "~/Demo_code"
setwd(path)
source("functions.R")
source("MCMC_DPM.R")
```
#### Data simulation

Set simulation design and optimization details:
```{r}
type <- 2  # 1 for simulating a single group, 2 for simulating mixture groups
source("SimDesign.R")   # Set simulation parameters

m       <- 20000  # Number of MC samples per candiate alpha
n2     <- 200    # Number of steps in the sequential optimization
indX_policy <- c(1)  # Indicator of the elements in X that will be a feature in the policy
q      <- length(indX_policy)+2    # Number of policy features
utility <- "red"   # Choose utility function: "red"/"ave"
```

Generate a fake dataset and also return a list of sufficient statistics X'X, X'Y and Y'Y for each patient:
```{r}
set.seed(806)
source("Sim_One_Dataset.R")
```
#### Model fitting 

Fit the DPM model:
```{r}
fit <- MCMC_DPM(base,nt,XX1,XY1,YY1,XX2,XY2,YY2,iters=5000,burn=3000,update=1000)
```

Select a subset of the MCMC posterior samples for policy search:
```{r}
iters <- dim(fit$b0)[1]
samps <- sample(1:iters,100,replace=FALSE)
  
B0  <- NULL
B1  <- NULL
B2  <- NULL
PR  <- NULL
for(draw in samps){
  B0 <- rbind(B0,fit$b0[draw,,])
  B1 <- rbind(B1,fit$b1[draw,,])
  B2 <- rbind(B2,fit$b2[draw,,])
  PR <- c(PR,fit$pg[draw,])
}
keep <- PR>0.01
B0   <- B0[keep,]
B1   <- B1[keep,]
B2   <- B2[keep,]
PR   <- PR[keep]
  
params_fit <- list(
  b0      = B0,
  b1      = B1,
  b2      = B2,
  tchols0 = t(chol(apply(fit$s0,2:3,mean))),
  s1      = mean(fit$s1),
  s2      = mean(fit$s2),
  prob    = PR/sum(PR))
```

####Policy search
Optimize the feature weights that minimize the opposite number of the value (equivalent to maximizing the value):
```{r}
source("optimization.R")
```

####Store the output
```{r}
# Estimate the threshold corresponding to the estimated optimal alpha
thresh  <- get.thresh(alpha_est,params_fit,m=50000,policy=riskscore,
                      indX_policy=indX_policy)
# Compute the value corresponding to the estimated optimal alpha using fitted model
v1      <- get.value(alpha_est,params_fit,m=1000000,thresh=thresh,policy=riskscore,
                     utility=utility,indX_policy=indX_policy)
# Compute the value corresponding to the estimated optimal alpha using oracle model
v2      <- get.value(alpha_est,params_or,m=1000000,thresh=thresh,policy=riskscore,
                     utility=utility,indX_policy=indX_policy)

cat("The estimated optimal feature weights alpha: ",alpha_est)
cat("The threshold: ",thresh)
cat("The value, standard error of the value, cost and standard error of the cost
    corresponding to the estimated optimal alpha using fitted model:\n",c(-v1[1],v1[2:4]))
cat("The value, standard error of the value, cost and standard error of the cost
    corresponding to the estimated optimal alpha using oracle model:\n",c(-v2[1],v2[2:4]))
```